---
title: "Mapping the Evidence Frontier with MLM501"
author: "Mahmood Ahmad"
date: "2026-03-04"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mapping the Evidence Frontier with MLM501}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(MLM501)
```

# Introduction
`MLM501` is an R-based suite for auditing evidence robustness across the Cochrane database. This vignette demonstrates the workflow from loading 2,373 analyses to simulating the **Net Clinical Benefit** of a diagnostic pathway.

## 1. The Global Evidence Audit
The core of the package is the `Cochrane Fragility Atlas (CFA)`. We begin by calculating the **MAFI 2.0** scores across all specialty groups.

```{r global-audit, eval=FALSE}
# Load the comprehensive audit database
audit_db <- calculate_global_audit_pro(MLM501_full_database)

# Filter for Cardiovascular "High Fragility" cohorts
cvd_fragile <- audit_db[audit_db$specialty == "Cardiovascular" & audit_db$MAFI > 0.6, ]
print(head(cvd_fragile))
```

## 2. Bayesian Credibility Check
For analyses classified as "High Fragility," we apply the Bayesian Engine to calculate 95% Credible Intervals for the fragility scores.

```{r bayes-check, eval=FALSE}
# Perform Bayesian stress-test on a target analysis
target <- cvd_fragile[1, ]
bayes_check <- calculate_bayesian_fragility(target$yi, target$vi)

# Result: Median MAFI with Bayesian uncertainty bounds
print(bayes_check)
```

## 3. Evidence Pathway Simulation
Finally, we bridge these findings into a clinical pathway to calculate the real-world impact.

```{r pathway-sim, eval=FALSE}
# Simulate a Cardio-Renal pathway
# Prevalence: 15%, HS-Troponin Sensitivity: 92%, Specificity: 88%, RR: 0.85
pathway <- simulate_pathway(
  prevalence = 0.15, 
  sensitivity = 0.92, 
  specificity = 0.88, 
  rr = 0.85, 
  harm_rate = 0.02
)

# Calculate Economic Value (NHS QALY metrics)
econ_impact <- calculate_economic_impact(pathway)
print(econ_impact$value_of_benefit_formatted)
```

# Conclusion
By integrating non-linear evidence decay and health-economic modeling, `MLM501` identifies the "Cost of Fragility" in healthcare.
